Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)

### 2018-03-07 paper.tex
reorganize

%% Title information
\title[Short Title]{Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
\subtitle{Filling the Gap between Abstracting Abstract Machines and Abstracting Definitional Interpreters}        %% \subtitle is optional
\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

  In this paper, we show their correspondence and how to syntactically transform small-step 
  abstracting abstract machines into big-step abstracting definitional 
  interpreters.
  The transformations include fusing, disentangling, refunctionalizing 
  and monadification (or un-CPS to direct-style with delimited continuation). 
  All of them properly handle the 
  collecting semantics and the non-determinism of abstract interpretation. 
  After each transformation, we also obtain an intermediary form of 
  abstract interpreter.
  Remarkably, refunctionalization sequentializes the abstract evaluation.
  And follow the idea that evaluation contexts are defunctionalized 
  continuations, we reveal how precise call/return match in control-flow 
  analysis can be obtained by refunctionalizing a small-step abstracting 
  abstract machine,
  as well as explain how it been lost by defunctionalizing the higher-order
  continuations into an firts-order data type.

@@

\item A new understanding of pushdown control-flow analysis by 
  refunctionalization.
  We present an abstract interpreter obtained from refunctionalizing
  an small-step abstracting abstract machine. 
  This abstract interpreter naturally has pushdown control-flow property
  because the refunctionalization forces us to sequentialize the 
  abstract exectuion.
  We also analyze its termination and soundness.

>>>>

%% Title information
\title[Short Title]{Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
\subtitle{Or Filling the Gap of Abstracting Abstract Machines to Abstracting Definitional Interpreters}        %% \subtitle is optional
\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

  In this paper, we show their correspondence and how to syntactically transform small-step 
  abstracting abstract machines into big-step abstracting definitional 
  interpreters.
  The transformations include fusing, disentangling, refunctionalizing 
  and monadification (or un-CPS to direct-style with delimited continuation). 
  All of them properly handle the 
  collecting semantics and the non-determinism of abstract interpretation. 
  After each transformation, we also obtain an intermediary form of 
  abstract interpreter.
  Remarkably, refunctionalization sequentializes the abstract evaluation.
  And follow the idea that evaluation contexts are defunctionalized 
  continuations, we reveal how precise call/return match in control-flow 
  analysis can be obtained by refunctionalizing a small-step abstract interpreter.
  as well as explain how it been lost by defunctionalizing the higher-order
  continuations into an firts-order data type.

@@

\item A new understanding of pushdown control-flow analysis by 
  refunctionalization.
  We present an abstract interpreter obtained from refunctionalizing
  an small-step abstracting abstract machine. 
  This abstract interpreter naturally enjoys pushdown control-flow property
  because the refunctionalization forces us to sequentialize the 
  abstract exectuion.
  We also analyze its correctness, soundness and termination.
